Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-07-08 analysis/paper/paper.Rmd
Further clarify raw data and metadata

Efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open-source code which are deposited in public repositories and can be run by anyone following the download of data and code.
Making the raw data FAIR means providing proper metadata for the resource.
The metadata define the resource that has been made available allowing for discovery and use by other interested parties.
That is, proper cataloguing and descriptions of the computational materials and data enable others to easily find and understand what the materials are.
Properly constructed metadata allow for interoperability by allowing both humans and machines to understand what the materials are that are included in the resources and make use of them more easily.
Metadata also protects the resource and its future availability by tracking the resource's lineage, describing the resources physical characteristics and behavior so that it can be replicated using future technologies.
That is, without metadata, the data are not FAIR and the computational materials lose value by not having good documentation.

>>>>

Efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open-source code which are deposited in public repositories and can be run by anyone following the download of data and code.
Making the raw data FAIR means providing proper metadata, a clear description of what the resource contains, how it can be used and other attributes about it that help users understand it.
The metadata further define the resource that has been made available allowing for discovery and use by other interested parties.
That is, proper cataloguing and descriptions of the computational materials and data enable others to easily find and understand what the materials are.
Properly constructed metadata allow for interoperability by allowing both humans and machines to understand what the materials are that are included in the resources and make use of them more easily.
Metadata also protects the resource and its future availability by tracking the resource's lineage, describing the resources physical characteristics and behavior so that it can be replicated using future technologies.
That is, without metadata, the data are not FAIR and the computational materials lose value by not having good documentation.
